.\documentclass[11pt]{article}

% Packages
\usepackage[letterpaper, margin=0.75in]{geometry}
\usepackage{parskip}        % adds space between paragraphs
\usepackage{hyperref}        % for clickable links
\usepackage{enumitem}        % better bullet lists
\usepackage{titlesec}        % customize section headings

% Format section headings
\titleformat{\section}
  {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titlespacing*{\section}{0pt}{3ex}{2ex}

% No page numbers
\pagestyle{empty}

% Custom commands for contact info
\newcommand{\contact}[3]{
  \begin{center}
    {\Large\textbf{#1}} \\[0.5em]
    #2 $\cdot$ \href{mailto:#3}{#3} $\cdot$ +91 70269 26525 \\[0.3em]
    \href{https://github.com/fargamer18}{github.com/fargamer18}
  \end{center}
}

\begin{document}

% ---------- Header ----------
\contact{Mohammed Faraz Khan}{Bangalore, India}{farazkhanmohammed32@gmail.com}

% ---------- Summary ----------
\section*{SUMMARY}
Passionate and hands-on Computer Science student with a strong focus on cybersecurity, systems programming, and applied machine learning. Experienced in building secure, real-world tools—from encrypted P2P file sharing to ML-based guidance systems and remote device administration. Eager to contribute to innovative teams as an intern in \textbf{cybersecurity, software development, or AI/ML} roles.

% ---------- Education ----------
\section*{EDUCATION}
\textbf{B.E. in Computer Science and Engineering} \\
NITTE MEENAKSHI INSTITUTE OF TECHNOLOGY, Bangalore, India \\
\textit{Aug 2022 -- June 2026}

% ---------- Skills (Two-Column Table) ----------
\section*{SKILLS}
\begin{tabular}{@{}p{0.22\textwidth} @{}p{0.75\textwidth}}
    \textbf{Languages:}         & Rust, Python, C, C++, Java, Kotlin, JavaScript/TypeScript, Dart, MATLAB \\
    \textbf{Machine Learning:}  & scikit-learn (MLP, Random Forest), LLMs, OCR, FastAPI, Flask, TensorFlow, OpenCV \\
    \textbf{Frameworks Tools:}& Flutter, Next.js, React, Tokio (Rust), Axum, Libp2p, Tkinter, Textual (TUI), Git, Docker, Bash \\
    \textbf{Cybersecurity}\newline\textbf{Systems:} & Zero-Trust Architecture, Cryptography (X3DH, Double Ratchet, AES/RSA), TLS, GPG, WebSockets, Linux (NixOS, Arch), Kernel Modules, Accessibility Services \\
\end{tabular}
% ---------- Technical Projects ----------
\section*{TECHNICAL PROJECTS}

\textbf{Zero Trust File Sharing} \hfill \textit{Rust, Flutter, Libp2p, AES-256-GCM} \\
\begin{itemize}[leftmargin=*, nosep]
  \item Built a peer-to-peer file sharing application with end-to-end encryption using X3DH key agreement and Double Ratchet algorithm for forward secrecy.
  \item Implemented a Rust backend (Tokio, Axum, Libp2p) and a cross-platform Flutter frontend, enabling secure file transfers without a central server.
\end{itemize}

\textbf{Student Guidance System (SGS)} \hfill \textit{Python, scikit-learn, Flask, JavaScript} \\
\begin{itemize}[leftmargin=*, nosep]
  \item Developed an integrated ML platform that predicts student career paths (Random Forest, \~89\% accuracy) and assesses mental health conditions (MLP Classifier, 82\% accuracy).
  \item Created a Flask API and a dark-themed JavaScript dashboard with interactive charts and PDF report export.
\end{itemize}

\textbf{Remote Agent System (RAT 2.0)} \hfill \textit{Python, Kotlin, Android SDK, WebSockets, TLS} \\
\begin{itemize}[leftmargin=*, nosep]
  \item Engineered a remote device control system for headless Android phones: Python GUI (Tkinter) controller + Android agent using MediaProjection and Accessibility services.
  \item Features live screen streaming, touch injection, shell commands, and TLS-encrypted WebSocket communication.
\end{itemize}

\textbf{Controller Emulator (TUI)} \hfill \textit{Python, Textual, vgamepad, evdev} \\
\begin{itemize}[leftmargin=*, nosep]
  \item Designed a terminal-based (Textual) application that maps keyboard input to a virtual gamepad, supporting Xbox, DualShock, and Wii profiles with a modal keybind editor.
  \item Implemented profile persistence (\texttt{profiles.json}) and cross-platform support (Windows via vgamepad, Linux via uinput/evdev).
\end{itemize}

\textbf{NixOS Install Manager} \hfill \textit{C, GPG, NixOS} \\
\begin{itemize}[leftmargin=*, nosep]
  \item Created a secure, C-based utility that manages NixOS system packages through a GPG-encrypted file, decrypting, editing, and re-encrypting before triggering \texttt{nixos-rebuild}.
  \item Employs trie data structures for safe package lookups and ensures secure memory handling.
\end{itemize}

% ---------- Additional Information ----------
\section*{ADDITIONAL INFORMATION}
\begin{itemize}[leftmargin=*, nosep]
  \item Ranked in several CTF competitions; active in the cybersecurity community.
  \item Fluent in terminal tools, packet analysis, and OSINT automation.
  \item Currently building tools for BadUSB payload deployment and automated reconnaissance.
\end{itemize}

\end{document}